Figures

### 2019-04-26 figures/07_model-selection.Rmd
add 2nd level coefficents

dt <- readRDS("../data/dt.rds") %>%
  dplyr::select("lagoslakeid", "hu4_zoneid", "tp", "ag_pct", "phosphorus_fertilizer_use")

@@

names(dt) <- gsub("_", "v", names(dt))

@@

# non-linear re
model_form <- bf(tp ~ bagvpct * agvpct, 
                 bagvpct ~ 1 + 
                   (1|hu4vzoneid), 
                 nl = TRUE)
nlprior <- c(prior(norma(0, 100), nlpar = "bagvpct"))

fit <- brm(formula = model_form, data = dt, 
           family = gaussian(), prior = nlprior)

summary(fit)
marginal_effects(fit)
conditions <- data.frame(hu4vzoneid = unique(dt$hu4vzoneid)[1])
rownames(conditions) <- unique(dt$hu4vzoneid)[1]
me_zone <- marginal_effects(fit, conditions = conditions, 
                            re_formula = NULL, method = "predict")
ran_ef <- as.data.frame(ranef(fit)$hu4vzoneid) %>%
  mutate(zoneid = rownames(.)) %>%
  dplyr::filter(zoneid == unique(dt$hu4vzoneid)[1])

plot(me_zone, ncol = 1)$agvpct + 
  ggtitle(unique(dt$hu4vzoneid)[1]) +
  geom_abline(intercept = 0, slope = 0.6899723 + 1.25)
# ranef slope + fixed slope

ranef(fit)

get_prior(formula = model_form, data = dt)

model_prior <- prior()

fit <- brm(formula = model_form, data = dt, prior = model_prior)

>>>>

dt <- readRDS("../data/dt.rds") %>%
  dplyr::select("lagoslakeid", "hu4_zoneid", "tp", 
                "ag_pct", "phosphorus_fertilizer_use", "soybeans")

@@

names(dt) <- gsub("_", "v", names(dt))
dt <- dplyr::filter(dt, !is.na(phosphorusvfertilizervuse), 
                    !is.na(soybeans))

@@

# non-linear re
model_form <- bf(tp ~ bagvpct * agvpct, 
                 bagvpct ~ 1 + 
                   (1|hu4vzoneid), 
                 nl = TRUE)
fit1 <- brm(formula = model_form, data = dt, 
           family = gaussian())

# non-linear re w/ 2nd level coeffs
model_form2 <- bf(tp ~ bagvpct * agvpct, 
                 bagvpct ~ 1 + phosphorusvfertilizervuse + soybeans +
                   (1|hu4vzoneid), 
                 nl = TRUE)
fit2 <- brm(formula = model_form2, data = dt, 
           family = gaussian())
---
loo1 <- loo(fit1)
loo2 <- loo(fit2)
loo_compare(loo1, loo2)

fit <- brm(formula = model_form, data = dt, 
           family = gaussian())

summary(fit2)
marginal_effects(fit2)
conditions <- data.frame(hu4vzoneid = unique(dt$hu4vzoneid)[1])
rownames(conditions) <- unique(dt$hu4vzoneid)[1]
me_zone <- marginal_effects(fit, conditions = conditions, 
                            re_formula = NULL, method = "predict")
ran_ef <- as.data.frame(ranef(fit)$hu4vzoneid) %>%
  mutate(zoneid = rownames(.)) %>%
  dplyr::filter(zoneid == unique(dt$hu4vzoneid)[1])

plot(me_zone, ncol = 1)$agvpct + 
  ggtitle(unique(dt$hu4vzoneid)[1]) +
  geom_abline(intercept = 0, slope = ran_ef$Estimate.bagvpct_Intercept + 
                broom::tidy(fit)$estimate[1])
